Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex\\ over domains with shellable triangulations

### 2024-07-04 main.tex
Update on Overleaf.

\subsection{Poincar\'e--Friedrichs inequalities over convex domains}
% See the collection at Lemma 3.24 : https://hal.science/hal-03226049/file/volI_hal.pdf

@@

Given a gradient vector field, we can reconstruct the original scalar function up to a constant by a well-understood procedure: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point. This defines a scalar potential. 
This shall be our inspiration for estimating the Poincar\'e constant over triangulated domains, which we achieve by an explicit construction of scalar potentials. 
After fixing a starting triangle, we construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods. This is achieved by a local patchwise construction of a potential and matching that local contribution to the global potential being constructed in intermediate steps. 
Consequently, the overall estimate depends on the local Poincar\'e constants, the mesh quality, and the depth of the recursion. 
\\

Towards this goal, we introduce quantitative measures for the geometric quality of triangulations,
which give an indication of the regularity of simplex shapes. 
Most of such \emph{shape measures} in the literature are based on geometric features, 
but we consider indicators based on affine transformations associated with the mesh;
this is because the properties of these transformations are what shows up in our estimates.

Whenever $T$ is an $n$-dimensional simplex 
\begin{align}\label{math:geometricshapemeasure}
    \kappa(T)
    := 
    \frac{ \diam(T)^{n} }{ n! \vol(T) }
    .
\end{align}
% TODO: Although this is fairly clear upon reading, we could specify in word that $\kappa(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\rho(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
Moreover, when $\calT$ is an $n$-dimensional simplicial complex, we introduce 
\begin{align}\label{math:moremeasures}
    \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T),
%     \qquad 
%     \delta(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \diam(T) }{ \diam(T') },
    \qquad 
    \rho(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \vol(T) }{ \vol(T') }.
\end{align}
Whenever $S,T$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{S,T} : S \rightarrow T$ denote the affine diffeomorphism 
that preserves $F$. We define 
\begin{align}\label{math:reflectionmeasure}
    \xi(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \| \Xi_{S,T} \|.
\end{align}
This indicator quantifies how much reflection across the shared face distorts the geometry. 
% TODO: I imagine that $\Delta^n$ is a reference simplex, but this has not been introduced earlier.

@@

\begin{lemma}\label{lemma:affinetransform}
    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism. Then 
    \begin{align*}
        \| \Jacobian \varphi \|
        \leq 
        \sqrt{n} \cdot \diam(T)
        ,
        \qquad 
        \| \Jacobian \varphi^{-1} \|
        \leq 
        \sqrt{2n^{n}} 
        % \frac{ n! \vol(T) } { \diam(T)^{n} }
        \kappa(T)^{-1}
        \diam(T)^{-1}
        .
    \end{align*}
\end{lemma}
\begin{proof}
    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of $\Jacobian\varphi$ in descending order.
    Then $\sigma_1/\sigma_n \leq \sigma_1^{n} / \det(\Jacobian\varphi)$. Hence 
    \[
        \diam(T) 
        \leq 
        \sqrt{2} \sigma_1 
        \leq 
        \sqrt{2} 
        \frac{ \sigma_1^{n} }{ \det(\Jacobian\varphi) } 
        \sigma_n
        \leq 
        \sqrt{2n^{n}} 
        \frac{ \diam(T)^{n} }{ n! \vol(T) } 
        \sigma_n
        .
    \]
    The desired result is thus evident. 
\end{proof}

\begin{lemma}\label{lemma:volumecomparison}
    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
    \begin{align*}
        \frac{ \vol(T_1) }{ \vol(T_2) }
        &\leq 
        \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
        \cdot 
        \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
        = 
        \kappa(T_1) \kappa(T_2)
        ,
        \\
        \diam(T_1)
        &\leq 
        \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        \diam(F)
        = 
        \kappa(T_1)
        \diam(F)
        .
    \end{align*}
    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism, then 
    \begin{align*}
        \| \Jacobian \Xi \|
        \leq 
        \sqrt{2n^{n+1}} 
        \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
        =  
        \sqrt{2n^{n+1}} 
        \frac{ \kappa(T_1) }{ \kappa(T_2) }
        .
    \end{align*}
\end{lemma}
\begin{proof}
    Let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
    Then $\vol(T_1) = h_1 \vol(F)/n!$ and $\vol(T_2) = h_2 \vol(F)/n!$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
    We estimate 
    % TODO: I am not 100% sure what that means. Is really the heights of F? I imagine this is rather the heights of simplices T_1 and T_2, isn't? Maybe the wording you use is standard and I simply don't know about it, if so, please ignore the comment! (I mean, I am probably being too pedantic here, what you mean is completely clear from the next sentence).
    % TODO: clarify the following inequalities
    \begin{align*}
        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} \diam(F),
        \\
        h_2 &\geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
        .
    \end{align*}
    The first estimate follows. 
    Let $h$ be the height of some face $F'$ other than $F$ in $T_1$. Then $h \leq \diam(F)$, and with similar arguments as before: 
    \begin{align*}
        \diam(F)
        \geq 
        h
        =
        n!
        \frac{ \vol(T_1) }{ \vol(F') }
        \geq 
        \frac{ n! \vol(T_1) }{ \diam(T_1)^{n} }
        \cdot 
        \diam(T_1)
        .
    \end{align*}
    That shows the second estimate. 
    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, we find 
    \begin{align*}
        \| \Jacobian \Xi \|
        &
        \leq 
        \sqrt{n} 
        \cdot 
        \diam(T_1)
        \sqrt{2n^{n}} 
        \frac{ n! \vol(T_2) } {\diam(T_2)^{n} } 
        \diam(T_2)^{-1}
        \\&
        \leq 
        \sqrt{n} 
        \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        \diam(F)
        \sqrt{2n^{n}} \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
        \diam(F)^{-1}
        \leq 
        \sqrt{2n^{n+1}}
        \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
        .
    \end{align*}
    All the desired results thus follow. 
    % Together with analogous estimates that swap the roles of $h_1$ and $h_2$, we find 
    % \begin{align*}
    %     \max\left( \frac{h_1}{h_2}, \frac{h_2}{h_1} \right)
    %     \leq 
    %     \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
    %     \cdot 
    %     \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
    %     .
    % \end{align*}
\end{proof}

@@

@@

\begin{example}
    Any simplex $T$ trivially has a shelling. The boundary complex $\partial \calT(T)$ has a shelling:
    in fact, any enumeration of the boundary faces of $T$ constitutes a shelling.
\end{example}
\begin{example}
    The standard triangulation of the $n$-dimensional cube, the Kuhn triangulation, is shellable. 
    % https://scholar.google.de/scholar?hl=de&as_sdt=0%2C5&q=kuhn+triangulation+shelling&btnG=
\end{example}

@@

\begin{lemma}
    Let $\calT$ be a $n$-dimensional manifold triangulation and $V \in \Vertices(\calT)$ be an inner vertex.
    Then $\patch_{\calT}(V)$ is shellable. 
\end{lemma}
\begin{proof}
    Without loss of generality, $V$ is the origin. 
    Any ray starting at $V$ intersects at most one vertex of $\patch_{\calT}(V)$.
    We can also assume that all boundary vertices of $\patch_{\calT}(V)$ to be unit vectors,
    which does not affect shellability. 
    The simplicial boundary complex of $\calT$ is the boundary complex of a convex polytope,
    and is thus shellable~\cite{ziegler2012lectures}. % TODO: cite exactly 
\end{proof}

@@

The wedge product (or exterior product) of alternating multilinear forms is a fundamental operation in exterior algebra. 
Given two alternating multilinear forms \( u_1 \in \Alt^{k}(V) \) and \( u_2 \in \Alt^{l}(V) \), 
their wedge product \( u_1 \wedge u_2 \) is a member of $\Alt^{k+l}(V)$
defined by the formula 
\[
    (u_1 \wedge u_2)(v_1, v_2, \ldots, v_{k+l}) 
    = 
    \frac{1}{k! l!} 
    % \sum_{ \pi \in S_{k+l}} 
    \sum_{ \pi } 
    \signum(\pi) 
    u_1( v_{\pi(  1)}, \ldots, v_{\pi(k  )} ) 
    u_2( v_{\pi(k+1)}, \ldots, v_{\pi(k+l)} ),
\]
for any \( v_1, v_2, \ldots, v_{k+l} \in V \).
Here, the sum runs over all permutations $\pi$ of the index set \(\{ 1, 2, \ldots, k+l \}\).
% Here, \( S_{k+l} \) denotes the symmetric group on \( k+l \) elements, and \( \signum(\pi) \) is the sign of the permutation \( \pi \). 
The exterior product is bilinear and associative, and satisfies 
\begin{align*}
    u_1 \wedge u_2 = (-1)^{kl} u_2 \wedge u_1,
    \quad 
    u_1 \in \Alt^{k}(V),
    \quad 
    u_2 \in \Alt^{l}(V).
\end{align*}
We use the interior product, which is in some sense dual to the exterior product, in a special case. Given $v \in V$ and $u \in \Alt^{k}(V)$, we let $v \lrcorner u \in \Alt^{k-1}(V)$ be defined as 
\begin{align*}
    (v \lrcorner u)( v_1, v_2, \ldots, v_{k-1} ) = u( v, v_1, v_2, \ldots, v_{k-1} ),
    \quad 
    v_1, v_2, \ldots, v_{k-1} \in V.
\end{align*}
We are interested only in the special case $V = \bbR^{n}$ of alternating forms over the $n$-dimensional Euclidean space. 
Here, it is customary to identify $\Alt^{k}(V)$ with the space of antisymmetric tensors in $k$ indices. 
Moreover, this particular setting comes with a canonical basis. 
We let \(\{\cartanx^1, \cartanx^2, \ldots, \cartanx^{n}\}\) be the canonical basis dual to the standard unit vectors.
This is a canonical basis of $\Alt^{1}(\bbR^{n})$. 
To define a canonical basis of $\Alt^{k}(\bbR^{n})$, 
we first introduce $\Sigma(k,n)$, the set of strictly ascending mappings $\sigma : \{1,\dots,k\} \rightarrow \{1,\dots,n\}$,
and introduce the basic $k$-alternators 
\begin{align*}
    \cartanx^{\sigma} := \cartanx^{\sigma(1)} \wedge \dots \wedge \cartanx^{\sigma(k)}, \quad \sigma \in \Sigma(k,n). 
\end{align*}
These define a basis of $\Alt^{k}(\bbR^{n})$.
Note that 
$\dim \Alt^{k}(\bbR^{n}) = \binom{n}{k}$. 
In particular, $\Alt^{k}(\bbR^{n})$ is the zero vector space whenever $k > n$.
% The dimension of the space of \(k\)-forms, denoted \(\bigwedge^k V\), is given by the binomial coefficient \(\binom{n}{k}\).

We notice that the standard scalar product on $\bbR^{n}$ gives rise to a scalar product on $\Alt^{1}(\bbR^{n})$,
which induces a scalar product on $\Alt^{k}(\bbR^{n})$.
The basic $k$-alternators are an orthonormal basis of $\Alt^{k}(\bbR^{n})$ with respect to that inner product.

>>>>

\subsection{Poincar\'e--Friedrichs inequalities over convex domains}

@@

Given a gradient vector field, we can reconstruct the original scalar function up to a constant by a well-understood procedure: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point. This defines a scalar potential. 
This serves as our inspiration for estimating the Poincar\'e constant over triangulated domains, which we achieve by an explicit construction of scalar potentials: 
after fixing a starting triangle, we construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods. 
\\

Towards this goal, we introduce quantitative measures for the geometric quality of triangulations. 
These indicate of the regularity of simplex shapes. 
Most of such \emph{shape measures} in the literature are based on geometric features, 
but we also consider indicators based on affine transformations associated with the mesh;
this is because the properties of these transformations are what shows up in our estimates.

We define the \textit{geometric shape measure} of any $n$-dimensional simplex $T$ as 
\begin{align}\label{math:geometricshapemeasure}
    \kappa(T)
    := 
    \frac{ \diam(T)^{n} }{ n! \vol(T) }
    .
\end{align}
% TODO: Although this is fairly clear upon reading, we could specify in word that $\kappa(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\rho(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
Moreover, when $\calT$ is an $n$-dimensional simplicial complex, we introduce 
\begin{align}\label{math:moremeasures}
    \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T),
%     \qquad 
%     \delta(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \diam(T) }{ \diam(T') },
    \qquad 
    \rho(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \vol(T) }{ \vol(T') }.
\end{align}
Here, $\kappa(\calT)$ is the geometric shape measure of the triangulation, and $\rho(\calT)$ is the maximal ratio of volumes between neighboring $n$-simplices. 
Whenever $S,T$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{S,T} : S \rightarrow T$ denote the affine diffeomorphism 
that preserves $F$. We define 
\begin{align}\label{math:reflectionmeasure}
    \xi(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \| \Xi_{S,T} \|.
\end{align}
This indicator quantifies how much reflection across the shared face distorts the geometry.

For the purpose of the usual scaling arguments, we introduce the reference simplex $\Delta^n \subseteq \bbR^n$ as the convex closure of the origin and the $n$ canonical unit vectors.

% DONE: I imagine that $\Delta^n$ is a reference simplex, but this has not been introduced earlier.

@@

@@

\begin{lemma}\label{lemma:affinetransform}
    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
    \begin{align*}
        \| \Jacobian \varphi \|
        \leq 
        \sqrt{n} \cdot \diam(T)
        ,
        \qquad 
        \| \Jacobian \varphi^{-1} \|
        \leq 
        \sqrt{2n} 
        % \frac{ n! \vol(T) } { \diam(T)^{n} }
        \kappa(T)^{\frac 1 n}
        \diam(T)^{-1}
        .
    \end{align*}
\end{lemma}
\begin{proof}
    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of the Jacobian $\Jacobian\varphi$ in descending order.
    The Jacobian determinant is the product of these singular values. 
    Thus, $\sigma_1/\sigma_n \leq \sigma_1 / \sqrt[n]{ \det(\Jacobian\varphi) }$ and 
    \[
        \diam(T) 
        \leq 
        \sqrt{2} \sigma_1 
        \leq 
        \sqrt{2} 
        \frac{ \sigma_1 }{ \sqrt[n]{ \det(\Jacobian\varphi) } } 
        \sigma_n
        \leq 
        \sqrt{2n} 
        \left( \frac{ \diam(T)^{n} }{ n! \vol(T) } \right)^{\frac 1 n}
        \sigma_n
        .
    \]
    The desired result is thus evident. 
\end{proof}

\begin{lemma}\label{lemma:volumecomparison}
    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
    \begin{align*}
        \frac{ \vol(T_1) }{ \vol(T_2) }
        \leq 
        % \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
        % \cdot 
        % \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
        % = 
        \kappa(T_1) \kappa(T_2)
        ,
        \qquad 
        \diam(T_1)
        \leq 
        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        % \diam(F)
        % = 
        \kappa(T_1)
        \diam(F)
        .
    \end{align*}
    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism, then 
    \begin{align*}
        \| \Jacobian \Xi \|
        \leq 
        \sqrt{2n^{n+1}} 
        \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
        =  
        \sqrt{2n^{n+1}} 
        \frac{ \kappa(T_1) }{ \kappa(T_2) }
        .
    \end{align*}
\end{lemma}
\begin{proof}
    Let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
    Then $\vol(T_1) = h_1 \vol(F)/n!$ and $\vol(T_2) = h_2 \vol(F)/n!$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
    We estimate 
    % TODO: I am not 100% sure what that means. Is really the heights of F? I imagine this is rather the heights of simplices T_1 and T_2, isn't? Maybe the wording you use is standard and I simply don't know about it, if so, please ignore the comment! (I mean, I am probably being too pedantic here, what you mean is completely clear from the next sentence).
    % TODO: clarify the first of the following inequalities
    \begin{align*}
        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} \diam(F),
        \\
        h_2 &= n! \frac{\vol(T_2)}{\vol(F)} \geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
        .
    \end{align*}
    The first estimate follows. 
    Let $h$ be the height of some face $F'$ other than $F$ in $T_1$. Then $h \leq \diam(F)$, and with similar arguments as before: 
    \begin{align*}
        \diam(F)
        \geq 
        h
        =
        n!
        \frac{ \vol(T_1) }{ \vol(F') }
        \geq 
        \frac{ n! \vol(T_1) }{ \diam(T_1)^{n} }
        \cdot 
        \diam(T_1)
        .
    \end{align*}
    That shows the second estimate. 
    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, we find 
    \begin{align*}
        \| \Jacobian \Xi \|
        &
        \leq 
        \sqrt{n} 
        \cdot 
        \diam(T_1)
        %
        % \sqrt{2n} \left( \frac{ n! \vol(T_2) } {\diam(T_2)^{n} } \right)^{\frac 1 n}
        \sqrt{2n} \kappa(T_2)^{\frac 1 n}
        \diam(T_2)^{-1}
        \\&
        \leq 
        \sqrt{n} 
        \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        \diam(F)
        % \sqrt{2n^{n}} \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
        \sqrt{2n} \kappa(T_2)^{\frac 1 n}
        \diam(F)^{-1}
        \leq 
        n\sqrt{2}
        \kappa(T_1)
        \kappa(T_2)^{\frac 1 n}
        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        % \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
        .
    \end{align*}
    All the desired results thus follow. % TODO: improve these results 
    % Together with analogous estimates that swap the roles of $h_1$ and $h_2$, we find 
    % \begin{align*}
    %     \max\left( \frac{h_1}{h_2}, \frac{h_2}{h_1} \right)
    %     \leq 
    %     \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
    %     \cdot 
    %     \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
    %     .
    % \end{align*}
\end{proof}

@@

\begin{example}
    Any simplex $T$ trivially has a shelling. The boundary complex $\partial \calT(T)$ has a shelling:
    in fact, any enumeration of the boundary faces of $T$ constitutes a shelling.
\end{example}
\begin{example}
    The standard triangulation of the $n$-dimensional cube by six tetrahedra, the Kuhn triangulation~\cite{kuhn1960some}, is shellable.~\footnote{We remark that Kuhn attributes this triangulation to Lefschetz~\cite{lefschetz2015introduction}.}
\end{example}

@@

\begin{lemma}
    Let $\calT$ be a $n$-dimensional manifold triangulation and $V \in \Vertices(\calT)$ be an inner vertex.
    Then $\patch_{\calT}(V)$ is shellable. 
\end{lemma}
\begin{proof}
    Without loss of generality, $V$ is the origin. 
    Any ray starting at $V$ intersects at most one vertex of $\patch_{\calT}(V)$.
    We can also assume that all boundary vertices of $\patch_{\calT}(V)$ to be unit vectors,
    which does not affect shellability. 
    The simplicial boundary complex of $\calT$ is the boundary complex of a convex polytope,
    and is thus shellable~\cite[Theorem~8.12]{ziegler2012lectures}. 
\end{proof}

@@

The wedge product (or exterior product) of alternating multilinear forms is a fundamental operation in exterior algebra. 
Given two alternating multilinear forms \( u_1 \in \Alt^{k}(V) \) and \( u_2 \in \Alt^{l}(V) \), 
their wedge product \( u_1 \wedge u_2 \) is a member of $\Alt^{k+l}(V)$
defined by the formula 
\[
    (u_1 \wedge u_2)(v_1, v_2, \ldots, v_{k+l}) 
    = 
    \frac{1}{k! l!} 
    % \sum_{ \pi \in S_{k+l}} 
    \sum_{ \pi } 
    \signum(\pi) 
    u_1( v_{\pi(  1)}, \ldots, v_{\pi(k  )} ) 
    u_2( v_{\pi(k+1)}, \ldots, v_{\pi(k+l)} ),
\]
for any \( v_1, v_2, \ldots, v_{k+l} \in V \).
Here, the sum runs over all permutations $\pi$ of the index set \(\{ 1, 2, \ldots, k+l \}\).
% Here, \( S_{k+l} \) denotes the symmetric group on \( k+l \) elements, and \( \signum(\pi) \) is the sign of the permutation \( \pi \). 
The exterior product is bilinear and associative, and satisfies 
\begin{align*}
    u_1 \wedge u_2 = (-1)^{kl} u_2 \wedge u_1,
    \quad 
    u_1 \in \Alt^{k}(V),
    \quad 
    u_2 \in \Alt^{l}(V).
\end{align*}
We use the interior product, which is in some sense dual to the exterior product, in a special case. Given $v \in V$ and $u \in \Alt^{k}(V)$, we let $v \lrcorner u \in \Alt^{k-1}(V)$ be defined as 
\begin{align*}
    (v \lrcorner u)( v_1, v_2, \ldots, v_{k-1} ) = u( v, v_1, v_2, \ldots, v_{k-1} ),
    \quad 
    v_1, v_2, \ldots, v_{k-1} \in V.
\end{align*}
We are interested only in the special case $V = \bbR^{n}$ of alternating forms over the $n$-dimensional Euclidean space. 
Here, it is customary to identify $\Alt^{k}(V)$ with the space of antisymmetric tensors in $k$ indices. 
Moreover, this particular setting comes with a canonical basis. 
We let \(\{\cartanx^1, \cartanx^2, \ldots, \cartanx^{n}\}\) be the basis dual to the canonical unit vectors.
This is a canonical basis of $\Alt^{1}(\bbR^{n})$. 
To define a canonical basis of $\Alt^{k}(\bbR^{n})$, 
we first introduce $\Sigma(k,n)$, the set of strictly ascending mappings $\sigma : \{1,\dots,k\} \rightarrow \{1,\dots,n\}$,
and introduce the basic $k$-alternators 
\begin{align*}
    \cartanx^{\sigma} := \cartanx^{\sigma(1)} \wedge \dots \wedge \cartanx^{\sigma(k)}, \quad \sigma \in \Sigma(k,n). 
\end{align*}
These define a basis of $\Alt^{k}(\bbR^{n})$.
Note that 
$\dim \Alt^{k}(\bbR^{n}) = \binom{n}{k}$. 
In particular, $\Alt^{k}(\bbR^{n})$ is the zero vector space whenever $k > n$.
% The dimension of the space of \(k\)-forms, denoted \(\bigwedge^k V\), is given by the binomial coefficient \(\binom{n}{k}\).

We notice that the canonical scalar product on $\bbR^{n}$ gives rise to a scalar product on $\Alt^{1}(\bbR^{n})$,
which induces a scalar product on $\Alt^{k}(\bbR^{n})$.
The basic $k$-alternators are an orthonormal basis of $\Alt^{k}(\bbR^{n})$ with respect to that inner product.
